---
title: "Assessment 1"
author: "Heeral s4653155"
date: '2022-03-03'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# RMarkdown editing 

*Interactive documents* are a new way to build Shiny apps. An interactive document is an **R Markdown** file that contains Shiny widgets and outputs. You write the report in markdown, and then launch it as an app with the click of a button. **R Markdown** is a file format for making dynamic documents with R. An **R Markdown** document is written in markdown (an easy-to-write plain text format) and contains chunks of embedded R code. 
To know more [Click here](https://rmarkdown.rstudio.com/lesson-8.htm)

```{r}
#install.packages("tidyverse")
library(tidyverse)

fastfood <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

head(fastfood,10)

#install.packages("knitr")
library(knitr)

kable(fastfood[1:10,])

kable(fastfood[1:10,1:5])
```

## Food Items with more than 1000 calories

```{r}

fastfood %>%
  filter(calories>1000)

```

## Do not eat this
Arranging observations with more than 40 in total_fat and more than 80 in total_carb in the descending order and save them to a new variable (dataset) called `dont_eat_this'

```{r}
dont_eat_this <- fastfood %>%
  filter(total_fat>40) %>%
  arrange(desc(total_fat))


dont_eat_this <- dont_eat_this %>%
  filter(total_carb>80)%>%
  arrange(desc(total_carb))
```

## Categorising food items
Showing details of food items which are heavy (>500 calories), low (<250 calories) and average(between 250 to 500 calories)

```{r}
fastfood <- fastfood %>%
  mutate(heavy_food = case_when(calories >= 500 ~ "heavy", calories < 250 ~ "low", T ~ "average"))
 
fastfood %>%
  count(heavy_food)
```

## Different types of Variables

```{r}
#install.packages("skimr")
library(skimr)

fastfood %>% skim()
```

## Number of dishes from each restaurant

```{r}
fastfood %>%
  count(restaurant) %>%
  arrange()
```

## Items in the menu

```{r}
fastfood %>%
  count(item)
```

## Average caleroies for each restaurant

```{r}
fastfood %>%
  group_by(restaurant) %>%
  summarise(mean_calories = mean(calories)) %>%
  ungroup() 
```



